Baseline centering problem

### 2018-11-15 paper/advup_uniquesol.tex

Let us check the behavior of this when $\gamma\to 1$. We know that
\begin{equation}
V^\pi(s)=\frac{\E_{\rho^\pi}r}{1-\gamma}+U^\pi(s)+O(1-\gamma)
\end{equation}
with $\rho^\pi$ the invariant distribution from $\pi$, and $U$ the
relative value function of $\pi$. Thus, the fixed point for $V$ is
\begin{equation}
V(s)=U^\pi(s)-\gamma \E_{\tilde \rho}U^\pi +O(1-\gamma)
\end{equation}
which converges when $\gamma\to 1$???

The TD step in that case is simply
\begin{equation}
\E_s \partial_\theta V(s) \left(
r(s,a)+\gamma(V(s')-V(\tilde s))-V(s)\right)
\end{equation}
ie we just bring $V(s)$ closer to $V(s')-V(\tilde s)$. This is the
simplest trick ever to remove constants...

>>>>

Let us check the behavior of this when $\gamma\to 1$. We know that
\begin{equation}
V^\pi(s)=\frac{\E_{\rho^\pi}r}{1-\gamma}+U^\pi(s)+O(1-\gamma)
\end{equation}
with $\rho^\pi$ the invariant distribution from $\pi$, and $U$ the
relative value function of $\pi$. Thus, the fixed point for $V$ is
\begin{equation}
V(s)=U^\pi(s)+\frac{1-\gamma-\alpha}{\alpha} \,\E_{\tilde \rho}U^\pi
+\frac1{\alpha} \E_{\rho^\pi}r+O(1-\gamma)
\end{equation}
which converges to $V(s)=U^\pi(s)-\E_{\tilde \rho}U^\pi+\frac1{\alpha}
\E_{\rho^\pi}r$ when $\gamma\to 1$.

The TD step in that case, with $\alpha=1$, is simply
\begin{equation}
\E_s \partial_\theta V(s) \left(
r(s,a)+\gamma(V(s')-V(\tilde s))-V(s)\right)
\end{equation}
ie we just bring $V(s)$ closer to $r+V(s')-V(\tilde s)$. This is the
simplest trick ever to remove constants... Let's call this \emph{relative
TD}. (TODO check if name is preoccupied.)

(In particular, with $\gamma=1$ one
has $\E_{\tilde \rho}V=\frac{1}{\alpha}\E_{\rho^\pi}r$. For instance, if $\tilde \rho$ is
just a single reference
state $\tilde s$ and $\alpha=1$ then 
$V(\tilde s)=\E_{\rho^\pi}r$.)
